A Note on Convergence Diagnostics for Multiple Imputation Algorithms

### 2019-12-14 Simulation/Writeup/NoteConvergence.Rnw
safe plots with ses

\subsection{Convergence Diagnostics}
% Add ``post-processing steps (e.g. aggregation computations, summary statistics, regressions on the simulation results) used to transform simulation outputs to reported results''. %, see \url{http://jsterman.scripts.mit.edu/docs/Rahmandad-Sterman%20Simulation%20Reporting%20Standards3.30%20update.pdf}.
We investigate convergence by extracting not only the imputed values of each MI procedure (where $t = T$), but also information from the intermediate iterations ($t = 1, 2, \dots, T$). The quantities of interest ($\theta$-values) are chain means and chain variances. We compute convergence diagnostics separately for each of the four variables in the dataset. \textbf{We report the maximum (absolute) value as the `worst linear predictor' of convergence [Rephrase or footnote??]}. $\widehat{R}$ is computed by implementing Vehtari et al.'s \citeyear{veht19} recommendations. $AC$ is computed with \pkg{stats} function \fct{acf}.

% 
% 
% extract chain means and chain variances per iteration $t$. From the MI algorithm Convergence diagnostics are computed for chain means and chain variances.   
% $\widehat{R}$ is computed within imputation chains: . The maximum value across variables within the same simulation is reported. 
% 
% autocorrelation (AC) is computed within imputation chains,  The AC of the variable with the highest absolute AC value is reported per simulation.

@@

$$\bar{Q} \pm 2.66 \times SE_{\bar{Q}},$$

where 2.66 is the quantile of a $t$-distribution with $m-1$ degrees of freedom, and $SE_{\bar{Q}}$ is the square root of the pooled variance estimate. From bias and CIW, we calculate empirical coverage rates. Coverage rate is the proportion of simulations in which $Q$ is between the bounds of the CI95\% around $\bar{Q}$.

@@

@@

>>>>

\subsection{Convergence Diagnostics}
% Add ``post-processing steps (e.g. aggregation computations, summary statistics, regressions on the simulation results) used to transform simulation outputs to reported results''. %, see \url{http://jsterman.scripts.mit.edu/docs/Rahmandad-Sterman%20Simulation%20Reporting%20Standards3.30%20update.pdf}.
We extract not only the imputed values of each MI procedure (where $t = T$), but also information from the intermediate iterations ($t = 1, 2, \dots, T$). The quantities of interest ($\theta$-values) are chain means and chain variances. We compute convergence diagnostics separately for each of the four variables in the dataset. \textbf{We report the maximum (absolute) value as the `worst linear predictor' of convergence [Rephrase or footnote??]}. $\widehat{R}$ is computed by implementing Vehtari et al.'s \citeyear{veht19} recommendations. $AC$ is computed with \pkg{stats} function \fct{acf}.
%%%%%%%%%%%%%%%%
%From each imputation chain, we extract imputed values, chain means and chain variances ($\theta$-values). $\theta$-values are information from the intermediate iterations ($t = 1, 2, \dots, T$). The quantities of interest ($\theta$-values) are . We compute convergence diagnostics separately for each of the four variables in the dataset. \textbf{We report the maximum (absolute) value as the `worst linear predictor' of convergence [Rephrase or footnote??]}. $\widehat{R}$ is computed by implementing Vehtari et al.'s \citeyear{veht19} recommendations. $AC$ is computed with \pkg{stats} function \fct{acf}.
%%%%%%%%%%%%%
% 
% 
% extract chain means and chain variances per iteration $t$. From the MI algorithm Convergence diagnostics are computed for chain means and chain variances.   
% $\widehat{R}$ is computed within imputation chains: . The maximum value across variables within the same simulation is reported. 
% 
% autocorrelation (AC) is computed within imputation chains,  The AC of the variable with the highest absolute AC value is reported per simulation.

@@

$$\bar{Q} \pm t_{(m-1)} \times SE_{\bar{Q}}, \text{ where } t_{(m-1)} = 2.66 \text{ if } \alpha = .05. $$

$t_{(m-1)}$ is the quantile of a $t$-distribution with $m-1$ degrees of freedom, and $SE_{\bar{Q}}$ is the square root of the pooled variance estimate. From bias and CIW, we calculate empirical coverage rates. Coverage rate is the proportion of simulations in which $Q$ is between the bounds of the CI95\% around $\bar{Q}$.

@@

\begin{figure}[h]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{Figures/conv_diag_SEs.pdf}
  }
  \caption{Convergence diagnostics over 1000 MCMC simulations.}
    \label{fig:conv2}
\end{figure}

@@

\begin{figure}[h]
  \resizebox{\textwidth}{!}{ %notice the \resizebox{} command
        \includegraphics{Figures/sim_diag_SEs.pdf}
  }
  \caption{Simulation diagnostics over 1000 MCMC simulations.}
    \label{fig:sim2}
\end{figure}
